Deep Gaussian Processes and Hierarchical Modeling with Functional Data: A Case Study in Cosmological Power Spectra

### 2024-08-28 paper/main.tex
remove a few outliers from plot to make the plots fit better

For additional variation, the values of $m_1, m_2, u_1,$ and $u_2$ are random variables where $m_1 \sim Uniform(0.5,1.5), u_1 \sim Uniform(1.5,2.5),$ and $m_2,u_2 \sim Uniform(0.6,1.4)$. For each simulated function and variance specification, we generate 20 values of $m_1, m_2, f_1, f_2$, and conditional on these values, we sample either 5 or 20 functional observations and estimate the underlying true function based on the observations.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=6in]{sims_logS.png}
    \caption{Boxplot of log scores across two different functions and covariance settings (lower is better). For each case, twenty random batches were simulated.}
    \label{fig:sims_logS}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=6in]{sims_MSE.png}
    \caption{Boxplot of MSEs across two different functions and covariance settings (lower is better). For each case, twenty random batches were simulated.}    \label{fig:sims_MSE}
\end{figure}

@@

In addition to simulated data, we investigate model fits the for different cosmological datasets (based on linear theory and/or runs from the Code for Anisotropies in the Microwave Background, CAMB). \textcolor{magenta}{We have looked at two sets of model runs, "LT" runs where there is an underlying ``true" value alongside 15 computer model runs, or the "CAMB" runs, where we only have a single output. The performance from the CAMB runs was better (with a 6-dimensional design space), and also did not require obtaining a posterior mean from multiple model runs. When looking at the CAMB runs on the $\Delta$ space, we see it generally is withing $\pm 5\%$ error.}

\begin{figure}[ht]
    \centering
    \includegraphics[width=6in]{plot_pca_CAMB.png}
    \caption{Proportion of $\Delta_{emu}$ vs. $\Delta_{holdout}$ for model runs 11-42 (excluding 27-28).}   
    \label{fig:pca_camb}
\end{figure}

>>>>

For additional variation, the values of $m_1, m_2, u_1,$ and $u_2$ are random variables where $m_1 \sim \text{Uniform}(0.5,1.5)$, $u_1 \sim \text{Uniform}(1.5,2.5)$, and $m_2,u_2 \sim \text{Uniform}(0.6,1.4)$. For each simulated function and variance specification, we generate 20 values of $m_1, m_2, f_1, f_2$, and conditional on these values, we sample either 5 or 20 functional observations and estimate the underlying true function based on the observations.

\begin{figure}[h]
    \centering
    \includegraphics[width=6in]{sims_logS.png}
    \caption{Boxplot of log scores across two different functions and covariance settings (lower is better). For each case, the boxplot is constructed from 20 random batches were simulated. Each column represents a function/variance specification pair, and each row shows results for batch sizes of either 5 (top) or 20 (bottom).}
    \label{fig:sims_logS}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=6in]{sims_MSE.png}
    \caption{Boxplot of MSEs across two different functions and covariance settings (lower is better). For each case, the boxplot is constructed from 20 random batches were simulated. Each column represents a function/variance specification pair, and each row shows results for batch sizes of either 5 (top) or 20 (bottom).}    
    \label{fig:sims_MSE}
\end{figure}

@@

In addition to simulated data, we investigate model fits the for different cosmological datasets (based on linear theory and/or runs from the Code for Anisotropies in the Microwave Background, CAMB). \textcolor{magenta}{We have looked at two sets of model runs, "LT" runs where there is an underlying ``true" value alongside 15 computer model runs, or the "CAMB" runs, where we only have a single output. The performance from the CAMB runs was better (with a 6-dimensional design space), and also did not require obtaining a posterior mean from multiple model runs. When looking at the CAMB runs on the $\Delta$ space, we see it generally is withing $\pm 5\%$ error. Regarding these results, compared to the results for the 8-dimensional LT runs which had less impressive predictive performance, I'm not sure if we will include details on one or the other.}

\begin{figure}
    \centering
    \includegraphics[width=6in]{plot_pca_CAMB.png}
    \caption{Proportion of $\Delta_{emu}$ vs. $\Delta_{holdout}$ for model runs 11-42 (excluding 27-28).}   
    \label{fig:pca_camb}
\end{figure}
